%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% GUIDEWIRE ---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Guidewire Software Inc.} % Organization
    {Krak贸w} % Location
    {Feb. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed the solution for sharding monolith application in Cloud environment using AWS (EC2, S3, ECR, RDS), Docker and Kubernetes.}
        \item {Prototyped and built several microservice applications using Java 11, Spring Boot, Groovy, PostgreSQL, Redis and TeamCity.}
        \item {Designed and developed a solution for automated transformation of Electronic Rating Content with Java8, Spring and Antlr.}
        \item {Implemented several solutions for processing and customising algorithms and data structures transformed by the application.}
        \item {Improved efficiency of transformation by managing CI/CD pipelines on GoCD and optimizing utilized libraries.}
      \end{cvitems}
    }
%---------------------------------------------------------

% Cherry Pick ---------------------------------------------------------
  \cventry
    {Java EE Developer} % Job title
    {Cherry Pick Sp. z o.o.} % Organization
    {Krak贸w} % Location
    {Feb. 2015 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed web-based enterprise solution for multimedia content management using
Java EE 7, Primefaces, PostreSQL, Hibernate and WildFly.}
		\item {Implemented new features for the financial reporting application using Spring, JSP, Bootstrap and MySQL.}
		\item {Maintained a production Java application and provided technical support for clients.}
        \item {Prototyped, designed and implemented a server-side of web/mobile
application for video streaming based on RESTful web service using J2EE technologies.}
      \end{cvitems}
    }
%---------------------------------------------------------

% Softnet  ---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Softnet Sp. z o.o.} % Organization
    {Krak贸w} % Location
    {Sep. 2013 - Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Implemented financial reporting web applications for coopera-
tive banking institutions using Java EE 6, Vaadin, Oracle Database, Hibernate, Glassfish, JasperReports}
	  \item {Developed monitoring and alerting software for bank supervisors.} 
	  \item {Supported implementation and maintenance of Java application as technical advisor.}
      \end{cvitems}
    }
%---------------------------------------------------------
% Softnet - Internship  ---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {Softnet Sp. z o.o.} % Organization
    {Krak贸w} % Location
    {Jul. 2013 - Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Developed CRM software using Java, Hibernate, Oracle Database and PL/SQL}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
