%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Courses and Certificates}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% AWS---------------------------------------------------------
	\cventry
    {} % Role
    {AWS Certified Solutions Architect – Professional} % Title
    {Amazon Web Services} % Location
    {Jan. 2025 – Jan. 2028} % Date(s)
    {}   
    
    \cventry
    {} % Role
    {AWS Certified Solutions Architect – Associate} % Title
    {Amazon Web Services} % Location
    {Nov. 2024 – Jan. 2028} % Date(s)
    {}   
    
    \cventry
    {} % Role
    {AWS Certified AI Practitioner} % Title
    {Amazon Web Services} % Location
    {Oct. 2024 – Oct. 2027} % Date(s)
    {}
  
  \cventry
   	{} % Role
    {AWS Certified DevOps Engineer - Professional} % Title
    {Amazon Web Services} % Location
    {Mar. 2024 – Mar. 2027} % Date(s)
    {} 

  \cventry
    {} % Role
    {AWS Certified Developer - Associate} % Title
    {Amazon Web Services} % Location
    {Jan. 2024 – Mar. 2027} % Date(s)
    {}
    
  \cventry
    {} % Role
    {AWS Certified SysOps Administrator – Associate} % Title
    {Amazon Web Services} % Location
    {Mar. 2021 – Mar. 2027} % Date(s)
    {}
   

% Bottega---------------------------------------------------------
  \cventry
    {A three-day expert workshop intended for enterprise application architects focused on: 
\begin{itemize}
  \item The Strategic Practices of Domain-Driven Design and EventStorming.
  \item Implementation of microservice architecture.
  \item The Tactical Practices of Domain-Driven Design and architecture. 
\end{itemize}\vspace*{-\baselineskip} } % Role
    {Software architecture masterclass} % Title
    {Bottega IT Minds} % Location
    {27th – 29th Mar 2019} % Date(s)
    {}

% Niebezpiecznik---------------------------------------------------------
  \cventry
    {Practical training organized by one of leading polish security audits provider. } % Role
    {Web Application security and penetration testing} % Title
    {Niebezpiecznik.pl} % Location
    {4th - 5th Feb 2019} % Date(s)
    {}



    
%---------------------------------------------------------
\end{cventries}
