%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% AWS -  ---------------------------------------------------------
  \cventry
    {Senior Cloud Application Architect} % Job title
    {Amazon Web Services, Inc. \break Generative AI Innovation \& Delivery, AWS Professional Services} % Organization
    {Warsaw, Poland (remote)} % Location
    {Apr. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Leading a projects as technical expert. Guiding the project’s technical architecture and mentor developers to ensure alignment with business goals and coding standards, resolve challenges as they arise. Collaborate with stakeholders to plan projects and maintain code quality through reviews and best practices.}
       \item {Design and implementation of cloud infrastructure and cloud-native applications that achieve essential business values across a spectrum of industries, including entertainment, travel, finance, the public sector and retail.}
      \end{cvitems}
    }


% AWS -  ---------------------------------------------------------
  \cventry
    {Cloud Application Architect} % Job title
    {} % Organization
    {Warsaw, Poland (remote)} % Location
    {Oct. 2020 - Mar. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Adapting AWS technologies to deliver scalable, cost effective Serverless and container-base cloud applications.}
       \item {Developing microservices using modern technologies, including Java, Kotlin, Typescript, Python. }
       \item {Managing infrastructure using Infrastructure As A Code processes with CDK, Terraform and CI/CD tools.}
       \item {Conducting thorough audits of solutions to offer recommendations for performance and cost optimization.}
       \item {Providing mentorship to development teams to enhance development processes and application architecture.}
      \end{cvitems}
    }

% GUIDEWIRE - 2 ---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Guidewire Software, Inc.} % Organization
    {Krakow, Poland} % Location
    {Dec. 2019 - Sep. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Enhancing functionality of Spring Boot microservices hosted on Kubernetes base on business requirements and technical analysis.}
        \item {Improving and automating the process of database migration from Oracle to Amazon Aurora PostgreSQL using AWS, Terraform and TeamCity.}
      \end{cvitems}
    }

% GUIDEWIRE - 2 ---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {} % Organization
    {San Francisco Bay Area, USA} % Location
    {May 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with a team tasked with the design and development of a suite of internal tools, utilizing JavaScript (NodeJS) and GoLang to enhance developer experience and establish company standards for cloud-based solutions.}
        \item {Contributed as a team member on the development of an internal Platform as a Service solution built on top of AWS and Kubernetes using Terraform. }
      \end{cvitems}
    }
%---------------------------------------------------------

% GUIDEWIRE - 1  ---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    { } % Organization
    {Krakow, Poland} % Location
    {Feb. 2016 - Apr. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing the solution for sharding monolith application in Cloud environment using AWS (EC2, S3, ECR, RDS), Docker and Kubernetes.}
        \item {Prototyping and building several microservice applications using Java 11, Spring Boot, Groovy, PostgreSQL, Redis and TeamCity.}
        \item {Designing and developing a solution for an automated transformation of Electronic Rating Content with Java 8, Spring and Antlr.}
        \item {Implementing several solutions for processing and customizing algorithms and data structures transformed by the application.}
        \item {Improving efficiency of transformation by managing CI/CD pipelines on GoCD and optimizing utilized libraries.}
      \end{cvitems}
    }
%---------------------------------------------------------

% Cherry Pick ---------------------------------------------------------
  \cventry
    {Java EE Developer} % Job title
    {Cherry Pick Sp. z o.o.} % Organization
    {Krakow, Poland} % Location
    {Feb. 2015 - Nov. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developing a web-based enterprise solution for content management using
Java EE 7, Primefaces, PostreSQL, Hibernate and WildFly.}
		\item {Improving new features for the financial reporting application using Spring, JSP, Bootstrap and MySQL.}
		\item {Maintaining a production Java application and provided technical support for clients.}
        \item {Prototyping and implementing a server-side of web/mobile
streaming application based on RESTful web service using J2EE technologies.}
      \end{cvitems}
    }
%---------------------------------------------------------

% Softnet  ---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Softnet Sp. z o.o.} % Organization
    {Krakow, Poland} % Location
    {Sep. 2013 - Jan. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Implementing financial reporting web applications for cooperative banking institutions using Java EE 6, Vaadin, Oracle Database, Hibernate, Glassfish, JasperReports}
	  \item {Developing monitoring and alerting software for bank supervisors. Supporting implementation and maintenance of Java application as a technical advisor.} 
      \end{cvitems}
    }
%---------------------------------------------------------
% Softnet - Internship  ---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {} % Organization
    {Krakow, Poland} % Location
    {Jul. 2013 - Aug. 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
       \item {Developing a CRM software using Java, Hibernate, Oracle Database and PL/SQL}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
